Mean and variance functions used to simulate Gaussian data

### 2018-12-04 analysis/gaussian_signals.Rmd
wflow_publish("gaussian_signals.Rmd")

```{r plot-mean-functions, fig.height=10, fig.width=6}
plot_grid(qplot(t,mu.sp,  geom = "line",xlab = "",ylab = "",main = "Spikes"),
          qplot(t,mu.bump,geom = "line",xlab = "",ylab = "",main = "Bumps"),
          qplot(t,mu.blk, geom = "line",xlab = "",ylab = "",main = "Blocks"),
          qplot(t,mu.ang, geom = "line",xlab = "",ylab = "",main = "Angles"))
# plot(t,mu.dop,xlab = "",ylab = "",type = "l",main = "Doppler mean function")
# plot(t,mu.blip,xlab = "",ylab = "",type = "l",main = "Blip mean function")
# plot(t,mu.cor,xlab = "",ylab = "",type = "l",main = "Corner mean function")
```

>>>>

```{r plot-mean-functions, fig.height=10, fig.width=6}
plot_grid(qplot(t,mu.sp,  geom = "line",xlab = "",ylab = "",main = "Spikes"),
          qplot(t,mu.bump,geom = "line",xlab = "",ylab = "",main = "Bumps"),
          qplot(t,mu.blk, geom = "line",xlab = "",ylab = "",main = "Blocks"),
          qplot(t,mu.ang, geom = "line",xlab = "",ylab = "",main = "Angles"),
          qplot(t,mu.dop, geom = "line",xlab = "",ylab = "",main = "Doppler"),
          qplot(t,mu.blip,geom = "line",xlab = "",ylab = "",main = "Blip"),
          qplot(t,mu.cor, geom = "line",xlab = "",ylab = "",main = "Corner"),
		  nrow = 4,ncol = 2)
```
